Pottery decor as networks on the Middle Niger

### 2024-06-10 analysis/paper/paper.Rmd

# Fractured and extrapolated diversity of Doupwil
  i <- decors_abs[,c(4)]|> 
 iNEXT(q=c(0), datatype="abundance")
 p1 <- ggiNEXT(i, type=1, facet.var="Assemblage")+
  labs(title = "Doupwil")

# Fractured and extrapolated diversity of Jenne-jeno
 i <- decors_abs[,c(8)]|> 
 iNEXT(q=c(0), datatype="abundance")
 p2 <-  ggiNEXT(i, type=1, facet.var="Assemblage")+
  labs(title = "Jenne-jeno")

>>>>

# Fractured and extrapolated diversity of Doupwil
  i <- decors_abs[,c(4)]|> 
 iNEXT(q=c(0), datatype="abundance")

 p1 <- ggiNEXT(i, type=1, facet.var="Assemblage")+
  labs(title = "Doupwil")

# Fractured and extrapolated diversity of Jenne-jeno
 i <- decors_abs[,c(8)]|> 
 iNEXT(q=c(0), datatype="abundance")

 p2 <-  ggiNEXT(i, type=1, facet.var="Assemblage")+
  labs(title = "Jenne-jeno")
